Discovering governing reactions from concentration data

### 2018-01-26 docs/manuscript.tex
f
wip

@@

	In this example it is demonstrated that given enough data, the original model can be recovered in the limit of the noise variance $\sigma^2\to 0$.

>>>>

	The second example deals with the second scenario of measurement and solves the minimization problem (\ref{method:minimizationproblem}) with regularization parameters being determined by cross validation.

	In each of the considered examples the library of ansatz reactions $\Theta$ contains
	\begin{colbox}{F8E0E0}
		introduce ansatz functions
	\end{colbox}

@@

	In this example it is demonstrated that given enough data, the original model can be recovered in the limit of the noise variance $\sigma^2\to 0$. To this end, we first solve
